### 2014-08-12 latex/phd_thesis.tex
Began section on typical analysis of (whole genome) bisulfite sequencing by moving some stuff from introduction. Then wrote about challenges of PCR duplicate detection.
Added filtering of wgbs data. Closes #7
Experimental design for identifying differential methylation. One-group DMC testing.
Began section on calling DMCs in two-group experiments

@@

bp & base pair \\
kb & kilobase = $1000$ bp \\
Mb & megabase = $1,000,000$ bp \\
Gb & gigabase = $1,000,000,000$ bp \\
WGBS & whole genome bisulfite sequencing \\
RRBS & reduced representation bisulfite sequencing \\
FDR & false discovery rate \\
DMR & differentially methylated region \\
DMC & differentially methylated cytosine \\

@@

@@

%\include{backgroundcorrect} % backgroundcorrect.tex

% etc.

>>>>

\newcommand{\R}{{\textbf{\textsf{R}}}}}

@@

bp & base pair \\
kb & kilobase = $1000$ bp \\
Mb & megabase = $1,000,000$ bp \\
Gb & gigabase = $1,000,000,000$ bp \\
WGBS & whole genome bisulfite sequencing \\
RRBS & reduced representation bisulfite sequencing \\
FDR & false discovery rate \\
DMR & differentially methylated region \\
DMC & differentially methylated cytosine \\
HMM & hidden Markov model \\
CNV & copy number variant \\
SE & single-end sequencing \\
PE & paired-end sequencing \\
indel & insertion or deletion \\

@@

\include{wgbs_analysis} % wgbs_analysis.tex

@@
